A comprehensive approach to analyzing environmental data with non-detects

### 2024-06-07 Rmarkdown/README.Rmd
readme update

where, in addition to the symbols defined above, $Half-T$ represents the positive-values t distribution and $Gamma$ the gamma distribution, parameterized by mean $\mu$ and shape parameter $\alpha$. The linear model $\beta_{site} X_{site}$ estimates a separate intercept for each site, where $X_{site}$ is the design matrix and $\beta_{site}$ the coefficients. The autocorrelation coefficient, $\phi^s$, and the residual at time $t-s$, $r_{t-s}$, define the dependence of each observation on the previous one, where $s$ is the spacing between adjacent observations [@trueman_comparing_2022; @simpson_modelling_2018].

@@

$$
(5)~~
\begin{align}
\text{likelihood:} \\
y \sim MultivariateNormal(\begin{bmatrix}\mu_1 \\ \ldots \\ \mu_D\end{bmatrix}, \Sigma) \\
\Sigma = \begin{bmatrix} \sigma_1 & \ldots & 0 \\ \vdots & \ddots & \vdots \\ 0 & \ldots & \sigma_D\end{bmatrix} R \begin{bmatrix} \sigma_1 & \ldots & 0 \\ \vdots & \ddots & \vdots \\ 0 & \ldots & \sigma_D\end{bmatrix} \\
\\
\text{priors:} \\
\mu_j \sim T(\mu_\mu=0,\sigma_\mu=10,\nu_\mu=3), \text{ for } \textit{j} = 1,..,D \\
\sigma_j \sim T(\mu_\sigma=0,\sigma_\sigma=10,\nu_\sigma=3), \text{ for } \textit{j} = 1,..,D \\
R \sim LKJcorr(2)
\end{align}
$$

>>>>

where, in addition to the symbols defined above, $Half-T$ represents the positive-valued t distribution and $Gamma$ the gamma distribution, parameterized by mean $\mu$ and shape parameter $\alpha$. The linear model $\beta_{site} X_{site}$ estimates a separate intercept for each site, where $X_{site}$ is the design matrix and $\beta_{site}$ the coefficients. The autocorrelation coefficient, $\phi^s$, and the residual at time $t-s$, $r_{t-s}$, define the dependence of each observation on the previous one, where $s$ is the spacing between adjacent observations [@trueman_comparing_2022; @simpson_modelling_2018].

@@

$$
(5)~~
\begin{align}
\text{likelihood:} \\
y \sim MultivariateNormal(\begin{bmatrix}\mu_1 \\\ \ldots \\\ \mu_D\end{bmatrix}, \Sigma) \\
\Sigma = \begin{bmatrix} \sigma_1 & \ldots & 0 \\\ \vdots & \ddots & \vdots \\\ 0 & \ldots & \sigma_D\end{bmatrix} R \begin{bmatrix} \sigma_1 & \ldots & 0 \\\ \vdots & \ddots & \vdots \\\ 0 & \ldots & \sigma_D\end{bmatrix} \\
\\
\text{priors:} \\
\mu_j \sim T(\mu_\mu=0,\sigma_\mu=10,\nu_\mu=3), \text{ for } \textit{j} = 1,..,D \\
\sigma_j \sim T(\mu_\sigma=0,\sigma_\sigma=10,\nu_\sigma=3), \text{ for } \textit{j} = 1,..,D \\
R \sim LKJcorr(2)
\end{align}
$$
